---
title: "Practicum 2 - Outcome 4"
author: "Chase Tarr, Karla Garibay Garcia, Travis Christy"
date: "5/6/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(randomizr)
library(DeclareDesign)
library(fabricatr)
library(kableExtra)
library(estimatr)
library(DT)
```

## Practicum 2: Measurement Strategy 


### **Outcome 4**: Increase community support and knowledge of the restoration program 


#### Measurement Goal & Measure

**Goal**: Assess the level of knowledge about the Sandy River Basin (SRB) restoration program over time

“Which of the following SRB restoration activities is the most important for rebuilding salmon and steelhead populations?"

a. Removal of invasive riparian vegetation
b. Increasing law enforcement to curb illegal fishing
c. Removal of barriers to restore aquatic habitat connectivity
d. Addition of naturally derived nutrients   


#### Source & Rationale & Unit

*Source*: Survey response data

*Rationale*: Community members’ knowledge of the restoration program’s strategic framework should be measured directly via a survey question that does not lead the respondent in any particular direction

*Unit*: Individual survey respondent


#### Responsibility & Frequency

*Responsibility*: Independent survey firm sampling random households within the SRB

*Frequency*: Annually


#### Declaring the population

Using demographic data of the six cities surrounding the SRB, we found the approximate number of households in each city.

City        Approximate # households 
----        ------------------------
1                     1900
2                     1250
3                      900
4                      700
5                      445
6                      390


#### Target Population & Challenges

*Target Population*: The SRB community aka the households across the 6 cities in the SRB.


#### DeclareDesign()

```{r}
set.seed(228)
knowledge_population <- declare_population(
  knowledge = add_level(N = 6,
                    baseline =
                      c(0.7,0.6,0.5,0.4,0.2,0.2)), # based on different sized cities within the SRB
  community_pop = add_level(N = c(1900,1250,900,700,445,390), # households 
                      know = draw_binary(baseline))) 
pop <- knowledge_population()
pop.vector <- c(1900,1250,900,700,445,390)

my_estimand <- declare_inquiry(mean(know),
                                 label = "Ybar")

```

```{r}
knowledge_research <- declare_assignment(prob = 0.7,
                               assignment_variable = "r",
                               legacy = T)

knowledge_research

knowledge_sampling <- declare_sampling(strata = knowledge,
                             strata_n = c(300,200,100,90,80,50), # number of households within each city that we estimate will respond to our knowledge survey
                             legacy = T)
```

```{r}
strata_weighted_mean <- function(data){
  data.frame(
    estimator_label = "strata_w_mean",
    estimand_label = "Ybar",
    n = nrow(data),
    stringsAsFactors = FALSE,
    estimate = data %>% 
      filter(r == 1) %>% 
      group_by(knowledge) %>% 
      summarize(mean = mean(know)) %>% 
      mutate(prop=pop.vector/sum(pop.vector)) %>% # 'prop' is a variable calculating the proportion of units in the population that are at a given city
      mutate(sub.mean = mean*prop) %>% 
      pull(sub.mean) %>% #summs all the weighed averages of knowledge within cities to get a weighed sample mean
      sum()
  )
}

```

```{r diagnosis, cache=TRUE}
knowledge_answer <- declare_estimator(
  handler = label_estimator(strata_weighted_mean),
  inquiry = my_estimand)

knowledge_design <- knowledge_population + my_estimand + knowledge_research + knowledge_sampling + knowledge_answer

knowledge_diagnosis <- diagnose_design(knowledge_design, sims = 100)

knowledge_diagnosis$diagnosands_df[,c(8,9,6,10)] %>% 
  kable()

```













